### 2015-03-19 latex/phd_thesis.tex
Missing includes
Temporarily remove chapter from draft
Figure fixing.
Minor fixes
Added methsim chapter to main .tex file.

@@

\author{{\bf \Large Peter Francis Hickey}\\\\
Submitted in total fulfilment of the requirements\\
of the degree of Doctor of Philosophy\\\\
November 2014\\\\
Department of Mathematics and Statistics\\
The University of Melbourne\\\\}

@@

* Some data in my thesis are mapped to hg18 and some to hg19.
* Include summary of notation?

>>>>

\usepackage{mathabx}

\usepackage{placeins}

@@

\author{{\bf \Large Peter Francis Hickey}\\\\
Submitted in total fulfilment of the requirements\\
of the degree of Doctor of Philosophy\\\\
March 2015\\\\
Department of Mathematics and Statistics\\
The University of Melbourne\\\\}

@@

\begin{itemize}
  \item Some data in my thesis are mapped to hg18 and some to hg19.
  \item Include summary of notation?
\end{itemize}
